PANCHANGE_analysis

### 2020-09-08 PANCHANGE_analysis.Rmd
Added import/renaming blocks for all the neuro blocks in the baseline questionnaires. GLAD/EDGI are confirmed to work. Awaiting NBR data.

Model 0b: Overlapping disorders, Unadjusted
```{r GAD retro Model 0b}
gad_retro_model0b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1b}
gad_retro_model1b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ retro Model 0b}
phq_retro_model0b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model 1b}
phq_retro_model1b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model 0b}
pcl_retro_model0b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1b}
pcl_retro_model1b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR retro Model 0b}
ocir_retro_model0b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model 1b}
ocir_retro_model1b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

>>>>

Model 0b: Overlapping disorders, Unadjusted
```{r GAD retro Model 0b}
gad_retro_model0b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1b}
gad_retro_model1b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ retro Model 0b}
phq_retro_model0b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model 1b}
phq_retro_model1b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model 0b}
pcl_retro_model0b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1b}
pcl_retro_model1b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR retro Model 0b}
ocir_retro_model0b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model 1b}
ocir_retro_model1b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)
